---
title: "Week3-Code Along: Binary logistic regression"
author: "Elmera Azadpour"
date: "1/20/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(jtools)
```

```{r}
penguins %>% 
  select(species, bill_length_mm:sex) %>% 
  ggpairs(aes(color = species))
```

Create a subset with only Adelie and Chinstrap penguins.
```{r}
adelie_chinstrap <- penguins %>% 
  filter(species %in% c("Adelie", "Chinstrap")) %>% 
  mutate(species = fct_drop(species))
```

Lets do a dataviz of those two species:
```{r}
ggplot(data = adelie_chinstrap, aes(x = body_mass_g, 
                                    y = flipper_length_mm)) + 
  geom_point(aes(color = sex)) +
  facet_wrap(~species) # sexual dimorphism present
# looks like chinstrap tend to be a little larger in flipper length
```

Binary logistic regression, including:
- body mass 
- flipper length
- penguin sex
```{r}
adelie_chinstrap_blr <- glm(species ~ body_mass_g + flipper_length_mm + sex,
                            data = adelie_chinstrap, 
                            family = "binomial")
```

Take a look at the outcomes
```{r}
adelie_chinstrap_blr #female is reference level
summary(adelie_chinstrap_blr)
# body mass: odds of this penguins being chinstrap is going down, the - sign indicates
# flipper length: as flipper length increases, odds of this being a chinstrap penguin is increasing, + sign
# sex: if a penguin is male, it is less likely to be a chinstrap (little weird)
```

Does the flipper length significance align with what we see visually from the data?
```{r}
ggplot(adelie_chinstrap, aes(x = species,
                             y= flipper_length_mm)) +
  geom_jitter(aes(color = sex))
# yes model is reflecting this
# as flipper length gets larger, its more likely that its a chinstrap penguin
```

What are the acutal probabilities of being Chinstrap for each of the existing observations in our adelie_chinstrap data frame?
```{r}
blr_fitted <- adelie_chinstrap_blr %>% 
  broom::augment(type.predict = "response") #fitted tells us the probability that it is a chinstrap penguin
```

plotting fitted probabilities
```{r}
ggplot(blr_fitted, aes(x = flipper_length_mm,
                       y = .fitted)) +
  geom_point(aes(color = sex, pch = species)) +
  geom_smooth(aes(color = sex), se = FALSE) +
  labs( x = "Flipper length (mm)",
        y = "Probability of outcome Chinstrap")
```
Plot model based on different variables:
```{r}
effect_plot(adelie_chinstrap_blr,
            pred = flipper_length_mm,
            y.label = "Probability of Chinstrap",
            interval = TRUE)

effect_plot(adelie_chinstrap_blr,
            pred = body_mass_g,
            y.label = "Probability of Chinstrap",
            interval = TRUE)
```

What's the probability that a female penguin weighing 3410 g with a flipper length of 192mm is a chinstrap?
```{r}
ex_1 <- predict(adelie_chinstrap_blr,
                data.frame(sex = "female",
                           body_mass_g = 3410,
                           flipper_length_mm = 192),
                type = "response")
ex_1

ex_2 <- predict(adelie_chinstrap_blr,
                data.frame(sex = "female",
                           body_mass_g = 4119,
                           flipper_length_mm = 222),
                type = "response")
ex_2
```

